\clearemptydoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Outline of the Thesis}

\begin{center}
	\huge{Outline of the Thesis}
\end{center}




%--------------------------------------------------------------------
\section*{Part I: Introduction and Theory}

\noindent {\scshape Chapter 1: INTRODUCTION}  \vspace{1mm}

\noindent  This chapter presents an overview of the thesis and its purpose. Furthermore, 
it will discuss the sense of life in a very general approach.  \\

\noindent {\scshape Chapter 2: TECHNICAL AND SCIENTIFIC FUNDAMENTALS }  \vspace{1mm}

\noindent   This chapter presents all the techincal and the scientific fundamentals that are required in order
understand the work done in this thesis\\

\noindent {\scshape Chapter 3: RELATED WORK }  \vspace{1mm}

\noindent   This chapter presents all the related work similar to the work done in this thesis, some comparisions
of approaches of different people and also comparisions of similar tools \\

%--------------------------------------------------------------------
\section*{Part II: Design and Development}

\noindent {\scshape Chapter 4: OVERVIEW}  \vspace{1mm}

\noindent  This chapter presents the whole developed system's overview and all the modules involved.

\noindent {\scshape Chapter 4: LOCALIZATION ALGORITHM}  \vspace{1mm}

\noindent  This chapter presents the localization algorithm that was developed
in order to detect the bugs which are present in the files other than the source files. 
It also helps in reducing the time required for detecting and localizing the bugs.

\noindent {\scshape Chapter 4: APPROACH}  \vspace{1mm}

\noindent  This chapter presents the appraoch that has be owned in order to 
achieve the goal.

\noindent {\scshape Chapter 4: IMPLEMENTATION}  \vspace{1mm}

\noindent  This chapter presents the whole implementation details about the developed tool.
%--------------------------------------------------------------------
\section*{Part III: Evaluation and Discussion}

\noindent {\scshape Chapter 5: EVALUATION}  \vspace{1mm}

\noindent  This chapter presents the requirements for the process. \\

\noindent {\scshape Chapter 6: DISCUSSION}  \vspace{1mm}

\noindent  This chapter presents the requirements for the process. \\

\noindent {\scshape Chapter 7: CONCLUSION}  \vspace{1mm}

\noindent  This chapter presents the requirements for the process. \\